# VIX

Outline

* Define the VIx
* Why is it useful?
* How stable has the vix been?
* Any noteworthy regimes?
* Can you get a "vix" like measurement for non-S&P things?
* Does the vix do a good job of predicting future volatility?
* What if you aggregated the "vix" by securities?
* Or looked at options on sector ETFs?



## What is the VIX?

Helpful Resources:

*  https://www.spglobal.com/spdji/en/vix-intro/
*  https://www.cboe.com/tradable_products/vix/faqs/


## To Do
* NAs interpolate?
* Slice up time into different regimes
* Market timing strategy where you buy when vix is high and sell when it's low.
* Showing a rolling, moving average
* Define the vix
* Summary Stats


<!-- Load Packages -->

```{r,message=FALSE,include=FALSE}

library(tidyverse)
library(data.table)
library(tidyquant)
library(DT)

```


```{r,include=FALSE}
# Function definitions

moving_average = function(numbers,window=5){
  
  data_length = length(numbers)
  result = rep(NA,data_length)
  
  for (index in window:data_length) {
    result[index] = mean(numbers[(index-window):index])
  }
  
  return(result)
}


```


## Download and Clean Data

We get the VIX data from FRED, and the S&P 500 comes from Yahoo Finance.

```{r,echo=FALSE}
vix_data = tq_get("VIXCLS",get = "economic.data",from = "1970-01-01")
sp500_data = data.table(tq_get("^GSPC",get = "stock.prices",from = "1900-01-01"))


```


```{r}
vix = data.table(vix_data)

vix[,lag_1:=shift(vix$price)]
vix[,delta:=round(price-lag_1,2)]
# vix$rolling_mean = moving_average(vix$price,15)

vix_mean = mean(vix$price,na.rm = TRUE)

# Dropping NAs. # Should probably interpolate instead?
vix = vix[complete.cases(vix)]
datatable(vix,filter = 'top')

```

### Graph Takeaways

1. The VIX is often above its longterm average of 20ish.
2. There are volatility regimes. Said differently, there appears to be autocorrelation in the vix.
3. Sometimes the vix gets ridiculously high.

```{r}

ggplot(vix,aes(date,price)) +
  geom_line(aes(color='VIX')) +
  geom_hline(yintercept = vix_mean,color='red',size=1) +
  labs(title='VIX') + 
  scale_color_manual(name='Legend',
                     breaks=c('VIX', 'Long-Term Average'),
                     values=c('VIX'='black', 'Long-Term Average'='red'))


```


Clearly, the correlation is high. What's the cleanest way to get the auto correlations of the 
past few lags?

```{r}

ggplot(vix,aes(lag_1,price)) + geom_point() 

```


Below looks like a simple random sample:

```{r}


ggplot(vix,aes(date,delta)) + geom_point() 

```




```{r}


avg_vix_by_year = vix[,.(avg_vix=mean(price)),year(date)]
ggplot(avg_vix_by_year,aes(year,avg_vix)) + geom_col()


```


```{r}


merge(vix,sp500_data,by='date')


```








